% !TEX root = main.tex
\section{Introduction}\label{sec:intro}


The automotive industry is rapidly %\del{and continuously} 
changing, driven by needs of 
electric/hybrid cars, autonomous driving, and connected cars. 
At the same time, new major players are emerging in the field, like Google\footnote{\url{https://www.google.com/selfdrivingcar/}},  %~\cite{Google},
Apple\footnote{\url{https://en.wikipedia.org/wiki/Apple_electric_car_project}}, %~\cite{Apple,Apple2},
 Tesla, and Uber, while Original Equipment Manufacturers (OEMs) are increasingly turning into software companies. 
Historically, software was introduced in cars to optimize the control of the engine. 
Today, according to industry experts\footnote{\url{https://tinyurl.com/y9jnoupd}}, 80\% to 90\% of the innovation in the automotive industry is based on electronics, a big part of which is software~\cite{ESEM2016}. 

%\ins{
Traditionally, automotive system development is characterized by a complex supply-chain.
The OEM relies on a large number of suppliers to produce parts of the vehicle, including electrical and software components.
These components are integrated by the OEM with a growing amount of in-house development.
This means that the knowledge and competence of building a car is spread across an ecosystem composed of several different companies, each with potentially different internal organizations, objectives, competences, constraints, cultures, languages, and geographical locations. 
%}

%\ins{
To manage this complexity, the V-model\footnote{Originally developed for the defense domain %by the German DoD 
- \url{www.v-modell-xt.de}} %\ins{
is the de-facto development method in the automotive domain as also implicitly suggested by the ISO 26262 functional safety standard~\cite{iso26262}.
Consequently, the overall development organization is split in different groups, both by abstraction and competence (e.g. top level requirements,
architecture, software development, mechanical parts). %\todo{Previous sentence is unclear.}
This can cause a silo effect that hinders information sharing and synergy. %}


%The V-model\footnote{Originally developed for defense applications by the German DoD - \url{http://www.v-modell-xt.de/}} is the de-facto development method in the automotive domain as also implicitly suggested by the ISO26262 functional safety standard~\cite{iso26262}. The consequence of that is on having 
%The complexity of the automotive domain naturally leads (driven by the V-model development method on having 
%different levels of abstractions and on splitting the organization in sections, each of them taking care of a specific level, e.g. top level requirements,
%architecture, design and software development, hardware, mechanical parts, etc. 
%\todo{the role of the V-model is unclear. If it is generally adopted by automotive industry, we could rephrase in (1) the V model is the standard de facto. (2) due to the complexity of the domain, the V-model causes a silos effect ... This causes separations that hinders infor sharing and synergy.})
%This can cause a silos effect and separations that hinder information sharing and synergy.

%Moreover, it is very impractical to produce in-house all parts comprising a vehicle. Normally, OEMs 
%ask suppliers to produce parts of the vehicle, and the number of suppliers involved in parallel development can easily reach a count of 50 different suppliers. 
%This means that the knowledge and competence of building a car is spread across an ecosystem composed of several different companies, each with potentially different internal organizations, objectives, competences, constraints, cultures, languages, and geographical locations. 

%\ins{
Due to an increasing market demand~\cite{olsson2012climbing} and the success of agile methodologies~\cite{laanti2011agile}, large-scale system development organizations adopt agile practices~\cite{jalali2010agile} such as continuous integration and delivery (CI\&D), which promise shorter time to market and improved quality~\cite{olsson2012climbing}.
OEMs in particular, do expect increased flexibility and shorter cycle times.
However, in order to fully benefit from these approaches, OEMs need to apply them %\ins{
beyond the scope of individual teams, towards the scope of the complete automotive system,  %}\del{system-wide} \todo{add short definition}\eric{bit reluctant to add a formal definition here. Does this improved characterization suffice?} 
and to some extent even across organizational boundaries in their (software) value-chain. %}
%\ins{
According to Hosseini et al.~\cite{Hosseini2016}, it is crucial to understand the intended degree of information to be shared between partners in the value-chain, especially with respect to accountability, openness, and efficiency~\cite{Ball2009}.
Hosseini et al. refer to this as \emph{transparency} and note that the crucial aspects for decision making are information accessibility and availability~\cite{Hosseini2016,Turilli2009}.
%\eric{Seems to break the flow. Consider mentioning this after the RQs, thus say first what we do, before saying what we do not do.}\ins{Moreover, it is quite usual in automotive software development to share code from different partners (typically binary code). In this setting, the source code becomes ``transparent"\eric{I disagree. The binary code is as far away from transparency as possible, usually protected from recompilition.} to all stakeholders. This should ease CI but may also lead to more legal problems w.r.t. product liability. In this paper we will not focus much in this aspect, and this would be an interesting future work direction.}
To our knowledge, this {critical perspective of transparency and legal contracts} has not been applied to inter-organizational CI\&D. %}
%Nowadays OEMs have an increasing and strong motivation
%to embrace system-wide Continuous Integration and Delivery (CI\&D) in order to improve
%in flexibility and cycle time, despite the challenges mentioned above. 
%Therefore, reducing time-to-marked and improving flexibility in the automotive domain necessarily need to involve different actors in the automotive ecosystems.
%Since automotive development relies on complex supply chains, the agility across company boundaries becomes a crucial concern, and suppliers will be increasingly required to continuously deliver software as part of the system development.

In this paper we investigate %\todo{what we claim here is not fully aligned with the RQs} 
%\del{what are the} 
challenges and impediments of inter-organizational CI\&D in automotive system-development
%scaling software engineering agility \todo{added SE: to make the SE relevance more evident} beyond the company boundaries.
%However, our hypothesis, which is beyond the motivation of this paper, is that {\bf closed contracts are a killer for cross-organizations CI\&D}.
, i.e. the collaboration between an OEM and one or more suppliers, where contributions from more than one organization are continuously integrated and compiled into a potential delivery to end-users.
%\del{We consider this to include cases, where suppliers continuously deliver working software towards an OEM as well as any challenges that need to overcome in order to integrate these and compile them into deliveries to vehicles in possession of end-users. }\pat{I don't know how to simplify this sentence. Difficult to understand.}\eric{better?}
Specifically, we focus on {\em legal contracts} that regulate the agreements between these companies 
%are mainly based on closed contracts.
and {\em {inter-organisational} transparency} intended as the degree/level of information that is shared between the various companies %\ins{
involved in the development and its associated value-chain. %} \del{in the ecosystem}. 
%\todo{we could replace ecosystem with 'involved in the development'} 
%Focusing on the engineering of the software of modern and near future vehicles, o
Our study %\del{aims at providing an answer to}
addresses the following research questions:

%We believe that a new way of working between a OEM and its
%suppliers is needed in order to seriously adopt organization-wide CI\&D in the automotive domain. This is because only a part of the software is produced in house.
%More specifically, the relation between the OEM and its suppliers should change from a contract-based relationship to a more
%collaborative one where the OEM and suppliers are part
%of the same ecosystem and collaborate for mutual benefit.
%More transparency and less (closed-)contract-based working will then
%be some of the key enablers for organization-wide CI\&D.
%
%In order to confirm or reject this hypothesis we formulated the following research questions: % and sub-research questions:

%\begin{itemize}
%\item {\bf RQ1}: What are the challenges, impediments, and opportunities of applying continuous
%integration, delivery, and deployment across the OEM and its suppliers in the
%automotive software ecosystem?
\begin{itemize}
%\item {\em RQ1: What is the impact on business model strategies?}
\item {\em RQ1:  What are risks and/or benefits of increasing %\del{inter-organizational} 
transparency {in an inter-organizational CI\&D setting}?}
\item {\em RQ2: {(How) can sufficient information be provided in inter-organizational CI\&D collaborations?}
%Is there a lack or overload of information that is exchanged across organizations\ins{, when they collaborate in an inter-organizational CI\&D setting}?
} 
\item {\em RQ3: Are contracts an impediment for scaling %\chg{agility}
{CI\&D} across company boundaries?} %, and 
%are industry-wide standards and processes shared among organizations an enabler?} 
\item {\em RQ4: Are industry-wide standards and processes shared among organizations an enabler{ for inter-organizational CI\&D}?}
%\todo{I am still not happy to have 2 questions in 1 RQ.}
%what are the challenges of changing this collaboration model?} %What are the risksbenefits of increasing inter-organisations transparency?} %ch existing concepts can benefit inter-organisational transparency?}
%\item {\em RQ3: What are the main challenges while improving inter-organisations transparency?}
%\item {\em RQ3: What can be the impacts on business model strategies?}
\end{itemize}
%\end{itemize}

To give an answer to these research questions we performed semi-structured interviews within \company{} 
and 
%Delphi 
one of their larger suppliers in the context of a pilot project within \company{}. % Volvo Cars.
This pilot project is experimenting a more open and transparent way of working between these two companies. Thus, this pilot project is an ideal setting for investigating the effects of changing the way of collaborating between OEMs and suppliers.  
The pilot project is a large and complex project with over 200 engineers and developers. 
% and engineers if one count all types . 
%There are close to 30 different SCRUM and Agile teams. %It is classified\todo{By whom? What does this mean?} as the highest degree of complexity that can be done between the companies. 
In an attempt to reduce the complexity, developers from both companies work in the same office space, and they are organized in about 30 different agile teams. %\todo{scrum is (!) agile: is the difference relevant?}
%\ins{We anticipate the main findings of the study below} \del
The main findings of our study are:\\
%\begin{itemize}
%\item 
\noindent {\em RQ1} - Inter-organisational transparency is not a necessary condition for inter-organizational CI\&D but considered as positive for various reasons. %and creates positive synergy effects in terms of efficiency, trust, and mutual understanding while avoiding useless stressful situations. Transparency is also considered positive in terms of increasing the overall the project quality. 
%\ins{
While strategies exist that facilitate information sharing  across organizations, the automotive industry experiences difficulties to share information, manage responsibilities, and intellectual properties at the pace required for CI\&D.\\ %}
%\item 
\noindent {\em RQ2} - Transparency has positive effects on increasing information sharing among the members of the project that belong to different companies. However, transparency as such does not help providing a holistic project overview. Finally, overload of information is unlikely to be considered a problem.\\
%\item 
\noindent {\em RQ3} - In their current form, contracts are an impediment for inter-or\-ga\-nisational CI\&D; however, they also help facilitating negotiations between different organizations. \\
%\item 
\noindent {\em RQ4} - Industry-wide standards and processes and open source initiatives are seen as positive for promoting collaboration, knowledge sharing, and communication.
%\end{itemize}
%The findings of the paper are ...\pat{findings}

%The biggest challenges that emerged are: 
%
%\begin{itemize}
%\item  The automotive industry experiences difficulties to share information in the ecosystem, as well as to manage responsibilities and Intellectual Property Rights (IPRs). 
%\item When the collaboration between different organizations is regulated though more ``open-contracts", it is not obvious  how to manage negotiations and responsibility sharing.
%\item Means and strategies to share a ``big picture" of the project among the different stakeholders should be identified. A holistic view of the project could be beneficial for all stakeholders and can increase project efficiency and quality. 
%\end{itemize}

%\pat{Rogardt: is the above enough or should I say something more}

%\pat{Rogardt might help here. I don't know much about this project and also, how much we can say?}

Note, that it is quite usual in the automotive software development to share code from different partners (typically: encrypted binary code). We leave the challenges related to these aspects, such as product liability, for future work.

%We are not considering the transparency of this code nor associated challenges such as product liability and leave these aspects for future work.


The paper is organized as follows. Section~\ref{sec:context} defines the context of the study. 
Section~\ref{sec:relatedWorks} presents related works.
Section~\ref{sec:researchMethod} describes the research methodology we followed in order to give an answer to the research questions.
Section~\ref{sec:results} presents the results of the study. Section~\ref{sec:discussion} discusses the main findings.  
The paper concludes in Section~\ref{sec:conclusion} with final remarks and directions for future work.

% \todo{Eric: Add some more information about transparency. Investigate papers such as ``Modeling and Reasoning About Information Quality Requirements''. Position this study as a way to understand practitioner perspective on this.}