\section{Research Method}\label{sec:researchMethod}

%\todo{Add a figure that illustrates the study process and individual outcomes.}

This section describes the research %\del{methodology}\ins
{method} used to address our research questions.
Our data collection is based on semi-structured interviews. 
The interview protocol follows the seven-stages approach by Kvale \& Brinkmann~\cite{Kvale2015Interviews}, which covers preparation, execution, and reporting. The seven stages are: Thematising, Designing, Interviewing, Transcribing, Analysing, Verifying, and Reporting. %The way we used them in our study is described in the rest of this section. 

%The interview results aim at providing in-depth analysis on the current situation, as well as explore the desired (future) situation. %The results also provide the foundation for the Reference Model\todo{What is that?}~\cite{Blessing:2009:DDR:1717807}. %The goal of this section is to provide a clear description of the interview process applied in this research to support and clarify the results and present the results.

%\subsection{Seven stages}

\noindent {\bf Thematising}: This phase decides on the purpose and subject matter, as well as the methods to be applied. {In our case,} the purpose of the interview survey is to require in-depth information on the topics of CI\&D %Continuous Integration \& Delivery 
and %\del{Ecosystem \&} 
Transparency in the automotive industry. %\del{These topics are discussed with representatives of Volvo Cars and its suppliers (Tier-1 and Tier-2).} % Also consultancy companies who work closely with the automotive industry are interviewed for this project.\todo{what do you mean "for this project"? delete?}

\noindent {\bf Designing}: %\del{The seven stages of the approach are designed for the study.} \ins
{This phase takes care of designing the seven stages of the approach specifically for the study.} The structure of the interview survey, transcribing details, analysis protocol~\cite{saldana2015coding}, verification, and reporting are discussed %\ins{
with each interviewee %} 
in detail, %\ins{, 
along with the request for permission to record and transcribe. %}. 
%\del{Beforehand, %\del{the}\ins
%{each} interviewee is informed on the interview details, topics and requested permission for the purpose of recording the conversation for the transcript.} %By doing this beforehand, 
%the interviewee is familiar with the topics and allows him or her to reflect on the research topics upfront.

\noindent {\bf Interviewing}: The interview has been structured as a semi-structured interview where open questions guide the interview process towards a list of goals that need to be achieved in the interview. Semi-structured interviews are very suitable for exploratory research~\cite{Runeson:2009:GCR:1519313.1519324} %\ins
{like ours}. 
We prepared an interview guide\footnote{\url{https://www.dropbox.com/s/esnehg0iz7ekksa/InterviewGuide.pdf?dl=0}} that organizes the interview in three categories of questions: introduction, main %\del{questions}\ins
{part}, and cool-off.
The {\em introduction} is meant to create context/background, and to provide and maintain an informal and interactive atmosphere. %For the purpose of the research, it was necessary that the interviewee is able to explain as much as possible about her or her knowledge and experience in the own field of expertise in a limited time span. 
The {\em main part} of the interview is aimed at the actual research. The questions aim to guide the interview, but be dynamic and interactive at the same time. This dynamic and interactive nature of interviewing is useful for exploration and development of interesting and unexpected ideas brought up by the interviewees, which are less possible with other (more structured) methodologies, such as questionnaire surveys.
At the end of the interview, or {\em cool-off}, we give time to each interviewee to ask some questions about the topics: these could be topics or themes that are not mentioned in the interview or could be important for the research. We selected the candidates to be interviewed within the pilot project by trying to cover different expertise and by selecting people that are knowledgeable about the topic.
An overview of the selected interviewees' information can be found in Table~\ref{tab:population}; %\chg{the years in brackets refer to industry experience, without brackets refer to experience in that specific role. When the number with brackets is missing means that the interviewees have been always working on this role.}{
the last column reports the years of industry experience in the current role and, if applicable, the total number of years of experience.%}

 \begin{table}[htb]
 \centering \small
 \begin{tabular}{|c|l|p{3cm}|l|}\hline
 {\bf No.} & {\bf Company} & {\bf Role within company} & {\bf Exp. in years}\\ \hline
 1 & \company{} & Project Manager RFQ project & 4+ (20+) \\ \hline
 2 & \company{} & Software Developer & 2 (3)\\ \hline
 3 & \company{} & Director of Strategy and Concepts & 2+ (26) \\ \hline
 4 & Tier-1 supplier & Chief Engineer & 2.5 (17)\\ \hline
 5 & Tier-1 supplier & System Lead & 10+ (18) \\ \hline
 6 & Tier-1 supplier & Software Configuration Manager & 4\\ \hline
 7 & Tier-1 supplier & Open Source and Community Manager & $<$1 (28)\\ \hline
 8 & Tier-1 supplier & Chief Executive Officer & 10+\\ \hline
 9 & Tier-1 supplier & Product Manager & 3 (13)\\ \hline
 10 & \company{} & Electrical System Architect & 2.5 (19)\\ \hline
 \end{tabular}
 \caption{Overview of interviewees}
 \label{tab:population}
 \vspace{-.4cm}
 \end{table}

%\del{Also an appointment is made with the interviewee to verify and validate the transcript.}

\noindent {\bf Transcribing:} Analyzing the interview results requires to transcribe the interview in a clear and precise manner. %\del{The interviewee and interviewer speak in English and the interview is held in English, hence, this is also the case for the transcript. Also the analysis or coding is done in English. }\ins
{%\chg{Both i}{I}
Interviews, transcripts, analysis, and coding are in English.} %\todo{add data and statistics about that.}

\noindent {\bf Analysing:} For the analysis of the interview results, a protocol is applied to code the interview transcripts, retrieve useful information and analyze it for the research. This is done by using the method explained by Saldana \cite{saldana2015coding}. The transcript is divided into parts that are smaller and easier to code. This could be words, phrases, paragraphs or sections. The goal of this analysis is to find keywords or uncover themes that can be of value for the research. The findings are managed in the coding section of a qualitative research tool, Atlas.ti\footnote{https://atlasti.com}. %\todo{add data and statistics about that.}
This tool is used to manage quotations and codes of transcripts. The quotations and codes describe the train of thoughts of the interviewees. This is used to organize each interview into datasets and to help supporting or negating propositions and research questions. All information that was relevant for the research was submitted as a quotation and connected to a code, including information that was not a direct answer to a research question or proposition. 
In order to group the codes, we have formulated a set of propositions that are then confirmed or negated by analysing the data collected through the semi-structured interviews we performed.
The propositions aim at helping eliciting the different facets of transparency and contract-based collaboration, and are based on knowledge acquired in numerous meetings with \company{}, with many suppliers within the NGEA and NGEA2 projects,
and in our multi-annual and established collaboration with these companies. 
%The codes were grouped into code groups to give an answer to one specific question, e.g. codes relevant to proposition 1 were clustered in code group ``Proposition 1". This is done to simplify the writing process of the findings for each individual research questions and propositions. 
This entire process made it easy to group all relevant quotations in an overview and to create a selective dataset. %\todo{add data and statistics about that.} 
This dataset was then further analysed to retrieve the answers on the questions of every interviewee. In addition, the dataset provides extra information that could benefit the findings for the specific question. This could be extra background information, another perspective on the question or maybe start a new discussion. 

The results of this process are captured in the findings, the answers to the research questions and the propositions.

%This is done by constant comparison with the research, literature study and transcript in mind. After analysing the transcripts and defining the preliminary codes, the final codes are defined based on relevance and importance to the research topics, repetition or codes explicitly mentioned as important. The final codes are then used to draw conclusions.

\noindent {\bf Verifying:} Verification activities include ascertaining the validity, reliability and generalizability of the findings. {\em Validity} refers to the question if the study investigates what was originally intended to~\cite{Kvale2015Interviews}. The purpose of the interviews is to gather from the interviewees insights and knowledge on the topics. The interview is semi-structured and the questions are intended as guidelines throughout the interview, so to safeguard validity. %The guidelines are not meant to be strict, so it allows also to meander to address other related topics. 
By applying the systematic and structured approach by Kvale and Brinkmann \cite{Kvale2015Interviews}, we aim to safeguard the {\em reliability} of conducting, analyzing and reporting the interview process. Further threats to validity, and how we mitigate them, are discussed in Section~\ref{sec:threatsToValidity}.

\noindent {\bf Reporting:} In this paper we report the results of the analysis and we answer our research questions. 
%and RQ1b defined in the Introduction\todo{revise RQs, and should answer them all}. The results also support defining the Reference Model, which in turn will lay the foundation of the (intended) Impact Model~\cite{Blessing:2009:DDR:1717807}. The Impact Model will be of advisory nature and will describe the desired, improved situation that is expected. 
Even though the study is performed within a single OEM, the supplier company collaborates with many other OEMs %\ins
{in a very similar way}. 
This %\del{gives the flavour that}\ins
{makes} the results of our study %\del{will probably generalize} \ins
{useful, and potentially generalizable} to the automotive domain. 
Moreover, the way automotive OEMs work with suppliers is common to many other domains, e.g. aviation. We expect that our results will be valuable also outside the automotive domain. Further studies, however, are needed, as discussed in Section~\ref{sec:threatsToValidity}.

%and this gives the These models\todo{plural?} are designed specifically for the domain of automotive software ecosystems. However, by abstracting the models it might be possible to apply them in other similar domains, such as aviation.

%\subsection{Analysis protocol}
%We conducted ten interviews with practitioners in a wide range of companies in the automotive software ecosystem. The interviews were transcribed and codified in Atlas.ti. This tool is used to manage quotations and codes of transcripts. The quotations and codes describe the train of thoughts of the interviewees in order to process them into feasible datasets and to help supporting or negating propositions and research questions. All information that was relevant for the research was submitted as a quotation and connected to a code, including information that was not a direct answer to a research question or proposition. The codes were grouped into code groups to give an answer to one specific question, i.e. codes relevant to proposition 1 were submitted in code group ``Proposition 1". This is done to simplify the writing process of the findings for each individual research questions and propositions. This entire process made it easy to group all relevant quotations in an overview and to create a selective dataset. This dataset was then further analysed to retrieve the answers on the questions of every interviewee. In addition, the dataset provides extra information that could benefit the findings for the specific question. This could be extra background information, another perspective on the question or maybe start a new discussion. 
%
%The results of this process are the findings, and the answers to the research questions and propositions.
